### 2022-01-14 newvariant.tex
Incremental progress

We start by taking the mean generation interval of the wild type to be $\Gw = 5\days$ \citep{ferretti2020quantifying} and the squared coefficient of variation of generation intervals to be $\kappa=0.2$ \citep{ferretti2020quantifying} for both the variant and the wild type.
As noted above, we assume throughout that the variant and the wild type can be approximated with Gamma distributions with equal $\kappa$, and only consider differences in the mean.
We evaluate the estimates of relative strength $\rho$ across a wide range of $\kappa$ from 0 (fixed-length generation intervals) to 1 (exponential distributions).
To further explore how inference depends on underlying epidemiological conditions, we consider five scenarios: (1) $\rw < \rv < 0$, (2) $\rw < \rv = 0$, (3) $\rw < 0 < \rv$, (4) $0 = \rw < \rv$, and (5) $0 < \rw < \rv$.
In all of these cases, we assume $\delta = \rv - \rw = 0.1\pday$ based on the observed relative growth rate of the Alpha variant in the UK \citep{davies2021estimated}.

>>>>

We start by taking the mean generation interval of the wild type to be $\Gw = 5\days$ \citep{ferretti2020quantifying} and the squared coefficient of variation of generation intervals to be $\kappa=0.2$ \citep{ferretti2020quantifying} for both the variant and the wild type.
As noted above, we assume throughout that the variant and the wild type can be approximated with Gamma distributions with equal $\kappa$, and only consider differences in the mean.
We evaluate the estimates of relative strength $\rho$ across a wide range of $\kappa$ from 0 (fixed-length generation intervals) to 1 (exponential distributions).
To further explore how inference depends on underlying epidemiological conditions, we consider five scenarios, all with $\delta = \rv - \rw = 0.1\pday$ (based on observations of the Alpha variant in the UK \citep{davies2021estimated}), and with increasing underlying $r$: (1) $\rw < \rv < 0$, (2) $\rw < \rv = 0$, (3) $\rw < 0 < \rv$, (4) $0 = \rw < \rv$, and (5) $0 < \rw < \rv$.
